An Automatic Verification Framework for Software Configurations

### 2016-05-06 OSDI/arch.tex
config: checker part

>>>>

\para{Checking.}
The checker is used to detect the rule violations in the configuration
files of interest. The inputs of checker are the learned rules 
and the target configuration file to verify.
Its outputs a report (as shown in $\S$\ref{sec-motiv}) about 
whether it finds any error, \eg, rule violations, or a suspicious value.
As shown in Figure~\ref{fig-overview},
there are two sub-modules in the checker. They are responsible for
checking rule violations and suspicious values, respectively.
\ennan{I really wanted to say we are using MaxSMT to check and rank
these errors ...}
In our experience, we find learned rules can be significantly reused
to check different configuration files, thus improving our usability.
